ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-18 pyked.tex
fix schema link, add text about testing

The basic user interface to the \ck{} file in \pk{} is through the
\pybox|ChemKED| class. The \pybox|ChemKED| class constructor takes the filename
of a \ck{} file or a Python dictionary containing the contents of a \ck{} file
as its argument. When the file or dictionary is loaded, it is validated to have
the correct format by the Python package Cerberus \autocite{cerberus}. The
schema used for validation of the \ck{} files is available publicly in the
source code repository for
PyKED\footnote{\url{https://github.com/pr-omethe-us/PyKED/blob/master/pyked/chemked_schema.yaml}}.

@@

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, \texttt{ruamel.yaml}~\autocite{ruamel_yaml} for parsing YAML
files, Cerberus for validating \ck{} files~\autocite{cerberus}, and
pytest~\autocite{pytest:3.0.1} for unit testing.
Travis-CI\footnote{\url{https://travis-ci.org/}} provides continuous integration
testing.

@@

%====================================================================
\section{Usage example}\label{sec:usage-example}

>>>>

The basic user interface to the \ck{} file in \pk{} is through the
\pybox|ChemKED| class. The \pybox|ChemKED| class constructor takes the filename
of a \ck{} file or a Python dictionary containing the contents of a \ck{} file
as its argument. When the file or dictionary is loaded, it is validated to have
the correct format by the Python package Cerberus \autocite{cerberus}. The
schema used for validation of the \ck{} files is available publicly in the
\texttt{schemas} directory of the PyKED source code
repository\footnote{\url{https://github.com/pr-omethe-us/PyKED/tree/master/pyked/schemas}}.
To ease extension of the schema to describe other experimental measurements, it
comprises multiple YAML files.

@@

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, \texttt{ruamel.yaml}~\autocite{ruamel_yaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for unit testing, and
Travis-CI\footnote{\url{https://travis-ci.org/}} provides continuous integration
testing (i.e., runs the test suite after any new changes are made or pull-requested).

@@

%====================================================================
\section{Usage examples}\label{sec:usage-example}
